Endogenous Politics and \\ the Design of Trade Institutions

### 2017-01-17 draft.tex
make absolutely essential changes to lit review

It still does not seem feasible to provide this flexibility at precisely the level that the shock impacts the government's preferences $\ga(s)$ if the WTO does not know the mapping from $s$ to $\ga$. What's more, this may provide an answer to why Safeguard measures have fallen out of use. If the real purpose is to provide an outlet for political pressure, I have demonstrated above that the current WTO-style Safeguards rules seem designed explicitly to discourage such rent-seeking behavior. Thus if other measures such as Anti-Dumping Duties are more susceptible to manipulation, it seems natural that lobbies' efforts would migrate there.

>>>>

It still does not seem feasible to provide this flexibility at precisely the level that the shock impacts the government's preferences $\ga(s)$ if the WTO does not know the mapping from $s$ to $\ga$. What's more, this may provide an answer to why Safeguard measures have fallen out of use.\footnote{This is by no means the only proposed explanation. See \Textcite{bown2002s} and \Textcite{sykes2003} for example.} If the real purpose is to provide an outlet for political pressure, I have demonstrated above that the current WTO-style Safeguards rules seem designed explicitly to discourage such rent-seeking behavior. Thus if other measures such as Anti-Dumping Duties are more susceptible to manipulation, it seems natural that lobbies' efforts would migrate there.

### 2017-01-17 intro.tex
make absolutely essential changes to lit review

This is one example of a design question whose answers are sensitive to assumptions about the endogeneity of political pressure. In order to examine this question and others, I use a simple model that is standard in the literature (e.g. \Textcite{bown2002}, \Textcite{bown2004}, \Textcite{bs2005}, \Textcite{martinvergote}, \Textcite{bagwell2009}, \Textcite{beshkar2010a}, \Textcite{ms2012a}, and \Textcite{ms2013}) and add an endogenously-determined element to the usual exogenously-determined political economy weights. Because of its tractability, this model can address a wide range of institutional design questions while also allowing endogenous politics to be taken into account in a repeated-game setting.\footnote{Repeated non-cooperative-game models of trade agreements have been considered by \Textcite{mcm86,mcm89}, \Textcite{dixit1987}, \Textcite{bs1990, bs1997a, bs1997b, bs2002}, \Textcite{kovthurs}, \Textcite{maggi99}, \Textcite{coatesludema}, \Textcite{ederington}, \Textcite{rosendorff}, \Textcite{bagwell2009}, and \Textcite{park}. \Textcite{buzard2013a} features a repeated-game model similar in spirit to the model under consideration here but focusing on questions of optimal punishments when the government is non-unitary.}

>>>>

This is one example of a design question whose answers are sensitive to assumptions about the endogeneity of political pressure. In order to examine this question and others, I use a simple model that is standard in the literature (e.g. \Textcite{bs2001}, \Textcite{bown2002}, \Textcite{bown2004}, \Textcite{bs2005}, \Textcite{martinvergote}, \Textcite{bagwell2009}, \Textcite{beshkar2010a}, \Textcite{ms2012a}, and \Textcite{ms2013}) and add an endogenously-determined element to the usual exogenously-determined political economy weights. Because of its tractability, this model can address a wide range of institutional design questions while also allowing endogenous politics to be taken into account in a repeated-game setting.\footnote{Repeated non-cooperative-game models of trade agreements have been considered by \Textcite{mcm86,mcm89}, \Textcite{dixit1987}, \Textcite{bs1990, bs1997a, bs1997b, bs2002}, \Textcite{kovthurs}, \Textcite{maggi99}, \Textcite{coatesludema}, \Textcite{ederington}, \Textcite{rosendorff}, \Textcite{bagwell2009}, and \Textcite{park}. \Textcite{buzard2013a} features a repeated-game model similar in spirit to the model under consideration here but focusing on questions of optimal punishments when the government is non-unitary.}
